---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAFARI

<!-- badges: start -->
<!-- badges: end -->

The R package **SAFARI** (**S**hape **A**nalysis **f**or **A**I-Reconstructed **I**mages) provides functions for reading, preprocessing, segmenting ROI, and extracting shape-based features in AI-reconstructed images.

## Description

**SAFARI** is an R package that consists of a collection of functions for 
image processing and shape analysis. The available functions allow users to 
segment regions of interest and extract quantitative shape descriptors in 
AI-reconstructed images, especially those produced from medical imaging 
modalities. 

## Installation

You may install the latest released version on CRAN by

```{r install, eval=FALSE}
install.packages("SAFARI")
```

## Development

The latest version of the package is under development at [GitHub](https://github.com/estfernandez/SAFARI). One may install it by 

```{r development, eval=FALSE}
## install.packages("devtools")
devtools::install_github("estfernandez/SAFARI")
```

## Dependencies

This package requires the use of `EBImage` from the
[Bioconductor](https://bioconductor.org/packages/release/bioc/html/EBImage.html)
project. One must install this package by

```{r depend, eval=FALSE}
## install.packages("BiocManager")
BiocManager::install("EBImage")
```

## Get Started

Examples are provided for the main functions. One may get started from those examples and the function documentation. We also provide a command-line tool for applications in the terminal.

```{r examples, eval=FALSE}
library(SAFARI)
?read.image           # read and preprocess reconstructed image
?binary.segmentation  # segmentation procedure
?compute.features     # feature extraction for an individual ROI
?rc.plot              # visualize binary or segmented images
```

## License

[GNU General Public License](https://www.gnu.org/licenses/) (≥ 3)
